Contextual Combinatorial Cascading Bandits

### 2016-01-21 contextual combinatorial cascading bandits.tex
update discussion part

1. Our setting generalizes theirs, and our results with restricted to theirs is of same order except log

2. there is also other problem that can't be explained in their model even if without context information

Our setting generalizes several existing works but not limited to them. Our setting generalizes cascading bandit and combinatorial bandit to involve position discount,

to involve context

there are cases that can not be fit into their

our method generalize Qin's method and has a regret bound proof.

network latency

If the latency of every edge $e$ follows exponential distribution with mean of $\theta_*^{\top}x_{t,e}$. We call the latency is {\it high} if it is larger than a threshold $\tau$. A path is blocked if some of its edges has high latency. So a path is unblocked with probability
$$
\prod_{k=1}^{|A|} (1 - \exp(-(\theta_*^{\top}x_{t,a_k^t})\tau).
$$

>>>>

In the above, we formulate the general setting of contextual combinatorial cascading bandit with position discount. This setting generalizes several existing results.

If our setting restricts to the setting of combinatorial cascading bandit \cite{kveton2015combinatorial}, our regret bound is of order $O\left(\frac{L}{f^*}\sqrt{nK}\ln(n)\right)$ which has an additional term $\sqrt{\frac{L\ln(n)}{f^*}}$ than their result; the reason is that the best regret bound for stochastic MAB is $O(\frac{\ln(n)}{\Delta})$, which has been achieved by a lot of methods, while the best regret bound for linear bandit is $O\left(\frac{\ln^2(n)}{\Delta}\right)$ by \cite{abbasi2011improved}.

If our setting restricts to contextual combinatorial bandit \cite{qin2014contextual}, the random variable $\bO_t$ of observed base arms is $|\bA_t|$, which the number of base arms in chosen action $\bA_t$, and the minimal probability $p^*$ of observing all base arms in chosen actions should always be $1$. So our regret bound is of the same order with theirs. Notice that when applying their setting, the bound $C$ for Lipschitz continuity in our problem should be $\sqrt{K}$.

Our setting generalizes several existing works but not limited to them. For example, in medical treatment, a patient will be recommended with a series of treatments. The patient has to take the treatments one by one, so the series of treatment actually is a list. Suppose the effect, after taking a treatment, is represented by a Beta random variable $\bw$ with a mean $w = \theta_*^{\top}x$, where $\theta_*$ is unknown linear coefficients and $x$ denotes the context, which might include the conditions of the patient and the properties of the treatment. We say that the treatment is successful if the effect $\bw$ is larger than a threshold $\tau$. So a treatment $a$ is successful with probability
\begin{equation}
\label{eq:betaTau}
1 - \frac{B(\tau; \alpha, \beta_0)}{B(\alpha, \beta_0)},
\end{equation}
where $B$ is the incomplete Beta function, $\alpha = \frac{\beta_0 w}{1- w} > 1$ and $\beta_0 > 1$ is a fixed number. We say that a series of treatment $A = (a_1, \ldots, a_{|A|})$ is successful (value $1$) if and only if all treatments in $A$ are successful. So the expected reward function is
$$
f(A, w) = \prod_{k=1}^{|A|} (1 - \frac{B(\tau; \alpha_{a_k}, \beta_0)}{B(\alpha_{a_k}, \beta_0)}),
$$
where $\alpha_{a_k} = \frac{\beta_0 w_{a_k}}{1- w_{a_k}}$ and $w_a = \theta_*^{\top}x_{a}$.

By the expression of $f$, it is a function of the expected reward $w$. Next, because $B(\tau; \alpha, \beta_0), B(\alpha, \beta_0)$ are decreasing with respect to $\alpha$ and $\alpha$ is in increasing with respect to $w$, then Eq.~\eqref{eq:betaTau} is increasing with respect to $w$. Therefore, the expected reward has the property of monotonicity. For the Lipschitz continuity, by the Lipschitz continuity of expected reward function, defined in Eq.~\eqref{eq:AndRewardFunc}, and the continuity of Beta function, we can get $f$ also satisfies the Lipschitz continuity.

Thus this expected reward function satisfies our setting but can not be fit into previous works. Similarly, a lot of such kind of reward functions, where the real reward is obtained by a second process of observed weight.

% network latency

% If the latency of every edge $e$ follows exponential distribution with mean of $\theta_*^{\top}x_{t,e}$. We call the latency is {\it high} if it is larger than a threshold $\tau$. A path is blocked if some of its edges has high latency. So a path is unblocked with probability
% $$
% \prod_{k=1}^{|A|} (1 - \exp(-(\theta_*^{\top}x_{t,a_k^t})\tau).
% $$
